%-------------------------
% Resume in Latex
% Author : Dylan Tompkins
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & #2 \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
		\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
		\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
	\textbf{\Huge \scshape Dylan Tompkins} \\ \vspace{1pt}
	\href{mailto:dltompki@outlook.com}{\underline{dltompki@outlook.com}} $|$
	\href{https://www.linkedin.com/in/dltompki/}{\underline{linkedin.com/in/dltompki}} $|$
	\href{https://github.com/dylantompkins}{\underline{github.com/dylantompkins}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{California Polytechnic State University}{San Luis Obispo, CA}
{Bachelor of Science in Software Engineering}{Sep. 2021 -- Jun. 2025}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Jr. Software Development Engineer}{Jan. 2023 -- Present}
{Amazon}{San Luis Obispo, CA}

\resumeSubSubheading
{Jr. Software Development Engineer II}{Nov. 2023 -- Present}
\resumeItemListStart
\resumeItem{Owned the design of multiple feature projects for an existing product}
\resumeItem{Currently responsible for handing off my previous project to one of the engineers I onboarded}
\resumeItem{Currently planning the implmentation of a feature I designed, for launch on an expedited timeline}
\resumeItemListEnd

\resumeSubSubheading
{Jr. Software Development Engineer I}{Jan. 2023 -- Nov. 2023}
\resumeItemListStart
\resumeItem{Owned the development, testing, and launch of a major OE project}
\resumeItem{Owned the onboarding of 2 fellow Jr. SDEs and 1 full-time SDE}
\resumeItem{Promoted at the first opportunity my mentor and manager had}
\resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Caddie and Member Services}{Jul. 2019 -- Sep. 2022}
{Oak Hill Country Club | San Luis Obispo Country Club}{Rochester, NY | San Luis Obispo, CA}
\resumeItemListStart
\resumeItem{Required to meet the high expectations that come along with a prestigious environment}
\resumeItem{Took initiative to continuously improve my performance, in the absence of formal training}
\resumeItem{Responsible for everything from providing course knowledge to creating an enjoyable social environment}
\resumeItem{Exceptional performance led to me being requested repeatedly by members and recognized by my supervisors as the top performer in my class}
\resumeItemListEnd

\resumeSubheading
{President, Software Lead, and Competition Robot Driver}{Sep. 2017 -- Jun. 2021}
{Greece Gladiators FIRST Robotics Team 1591}{Rochester, NY}
\resumeItemListStart
\resumeItem{Promoted to Software Lead in second season, elected President by peers in third season}
\resumeItem{Created organization-wide and software specific communication and task management
	systems to greatly increase team productivity and efficiency}
\resumeItem{Trained and mentored peers in a variety of technical disciplines, including software, electrical,
	manufacturing, CAD, communication, organization, and leadership}
\resumeItem{Implemented complex automations and driver assistance features including PID controllers
	and computer vision, the source code for which can be found on my LinkedIn, under Projects}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Dyce} $|$ \emph{SLO Hacks 2022}}{April 2022}
\resumeItemListStart
\resumeItem{Received awards for Best Beginner Hack and Best Use of Google Cloud Platform}
\resumeItem{Created a location-based game using Flutter for the frontend, Firebase to host on the web, and Open Street Map}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Contact Tracer} $|$ \emph{Code: Buffalo Hackathon}}{April 2020}
\resumeItemListStart
\resumeItem{Received an honorable mention award}
\resumeItem{Created a contact tracing mobile app using a local SQLite database and the Google Maps API}
\resumeItemListEnd

\resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		            \textbf{Languages}{: Java, Python, C, SQL, TypeScript, Dart} \\
		            \textbf{Frameworks}{: React, Node.js, Angular, JUnit, Flutter, Spring} \\
		            \textbf{Developer Tools}{: Git, Docker, Linux, AWS, Google Cloud Platform, VS Code, IntelliJ, Neovim} \\
		            \textbf{Application Categories}{: Full-stack Web, Mobile, Robotics}
		      }}
\end{itemize}


%-------------------------------------------
\end{document}
